---
title: "Avocado"
author: "Benjamin"
date: "2024-04-01"
output: html_document
---

## Setting up my environment
```{r setup, include=FALSE}
 library("tidyverse")
```

## Avocado Consumption

This is avocado document. showing the differences in the consumption of the two types: **conventional** and **organic** avocado.

```{r sum of Total Volume}
geeks <- c(15087220911,436181682.1)
labels <- c("Conventional","Organic")
piepercent <- round(100*geeks/sum(geeks), 1)
pie(geeks, labels = piepercent, main = "SUM of Total Volume", col = rainbow(length(geeks)))
legend("topleft", c("Conventional","Organic"),cex = 0.8, fill = rainbow(length(geeks)))
```

```{r SUM of Average Price, echo=FALSE}

geeks<- c(10568.27,15089.43)
labels<- c("Conventional,Organic")
peipercent <- round(100*geeks/sum(geeks), 1)
pie(geeks,labels = piepercent,main="SUMof AveragePrice", col= rainbow(length(geeks)))
legend("topleft", c("Conventional" , "Organic"),cex = 0.8, fill = rainbow(length(geeks)))
```

Summary
   From the above charts, a greater part of *conventional* avocado was sold in comparison to the *organic* type, while the Organic has a higher Price which may be the reason for the fewer quantity sold.
Recommendation
   Since the consumer prefer to buy the conventional type, i advice that more of it should be stocked and very few of the organic type should be stocked.


Recommendation:

  Since the consumer prefer to buy the conventional type, i advice that more of it should be stocked and very few of the *organic* type should be stocked.
